Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-03-03 paper/1_Initial/manuscript.qmd
fix hierarchy

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    roles:
      - Project administration
      - Data curation
      - Formal Analysis
      - Investigation
      - Visualization
      - Writing – original draft
      - Writing – review & editing
    affiliations:
      - id: "id1"
        name: "University of Sussex"
        department: "School of Psychology"
        city: "Brighton"
        country: "UK"
        postal-code: "BN1 9RH"
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
  #   #   - Writing – review & editing
  # - name: Magdalena Pfaff
  #   orcid: 0009-0006-2386-7936
  #   affiliations:
  #     - ref: "id1" 
  # - name: Dominique Makowski
  #   corresponding: true
  #   orcid: 0000-0001-5375-9967
  #   email: D.Makowski@sussex.ac.uk
  #   url: https://realitybending.github.io/
  #   roles:
  #     - Conceptualization
  #     - Data curation
  #     - Formal Analysis
  #     - Funding acquisition
  #     - Investigation
  #     - Methodology
  #     - Project administration
  #     - Resources
  #     - Software
  #     - Supervision
  #     - Validation
  #     - Visualization
  #     - Writing – original draft
  #   affiliations:
  #     - ref: "id1"
  #     - name: "University of Sussex"
  #       department:  "Sussex Centre for Consciousness Science"
author-note:
  disclosures:
    gratitude: |
      ::: {.callout-note icon=false appearance="simple"}
      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
      :::
abstract: |
  Blabla the abstract blabla.
keywords: [keyword1, keyword2, keyword3]
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    include-in-header:
      - text: |
          \usepackage{lscape}
  apaquarto-docx: default
  apaquarto-html: default
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

@@

**Note to dom: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor. The low correlations of NW and ND with this general factor indicate that these dimensions do not contribute significantly to the measurement of general interoceptive awareness. Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.**

@@

**TODO: can you update the fig. 1's box (assessmeent of related traits) to remove the question marks and put the the stronger interoception correlates. -- > I have put somatic symptoms but can also change to anxiety or depression?**

<!-- **anything else?**. TO BE COMPLETED -- to be determined -->

@@

**Note to dom: just to confirm all of your samples are from unpublished papers tight ?**

@@

\input{../../analysis/figures/table2.tex}

#### Statistical analysis

@@

## Average correlations

@@

#### Correlations with body measures
<!-- Alexithymia -->
Alexithymia was assessed in the samples with the Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity] and the Toronto Alexithymia Scale [TAS, @bagby1994twenty].

@@

#### Correlations with mood measures

@@

#### Correlations with psychopathology measures

@@

#### Correlations with personality measures

@@

#### Correlations with other measures

@@

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Meta-analysis"
author:
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    roles:
      - Project administration
      - Data curation
      - Formal Analysis
      - Investigation
      - Visualization
      - Writing – original draft
      - Writing – review & editing
    affiliations:
      - id: "id1"
        name: "University of Sussex"
        department: "School of Psychology"
        city: "Brighton"
        country: "UK"
        postal-code: "BN1 9RH"
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
  # - name: Magdalena Pfaff
  #   orcid: 0009-0006-2386-7936
  #   affiliations:
  #     - ref: "id1" 
  # - name: Dominique Makowski
  #   corresponding: true
  #   orcid: 0000-0001-5375-9967
  #   email: D.Makowski@sussex.ac.uk
  #   url: https://realitybending.github.io/
  #   roles:
  #   affiliations:
  #     - ref: "id1"
  #     - name: "University of Sussex"
  #       department:  "Sussex Centre for Consciousness Science"
author-note:
  disclosures:
    gratitude: |
      ::: {.callout-note icon=false appearance="simple"}
      :::
      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
abstract: |
  Blabla the abstract blabla.
keywords: [keyword1, keyword2, keyword3]
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    include-in-header:
      - text: |
          \usepackage{lscape}
  apaquarto-docx: default
  apaquarto-html: default
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

**TODO: more detailed caption for the graph below. A good caption typically repeats and summarizes info from the text. E.g., "The different modalities of interoception can be measured in a variety of ways, directly and indirectly, ..."**

@@

@@

@@

@@

<!-- Note: this table is generated during data analysis -->
\input{../../analysis/figures/table2.tex}

#### Data Analysis

@@

#### Average correlations

@@

##### Correlations with body measures

<!-- Alexithymia -->
Alexithymia was assessed in the samples with the Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity] and the Toronto Alexithymia Scale [TAS, @bagby1994twenty].

@@

##### Correlations with mood measures

@@

##### Correlations with psychopathology measures

@@

##### Correlations with personality measures

@@

##### Correlations with other measures

@@

**TODO: integrate the following**
**Note to dom: @ferentzi2021examining suggests that all MAIA dimensions, except for Not-Worrying and Not-Distracting, relate to a general interoceptive awareness factor. The low correlations of NW and ND with this general factor indicate that these dimensions do not contribute significantly to the measurement of general interoceptive awareness. Instead, NW appears to measure low emotionality or neuroticism, while ND does not capture a coherent underlying structure.**
